%-------------------------
% Resume in Latex
% Author : Mohammad Ganji
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{-6pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}
\newcommand{\aboutItem}[1]{
  \item\small{
    {#1 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {#1} & {\color{dark-grey}\small #2 \hspace{1pt} $|$ \hspace{1pt} #3} \vspace{1pt}\\ % top row of resume entry
    \end{tabular*}\vspace{-6pt}
}

% \newcommand{\resumeProjectHeading}[2]{
%     \item
%     \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%       #1 & {\color{dark-grey}} \\
%     \end{tabular*}\vspace{-4pt}
% }

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}


% HEADER COMMANDS
\newcommand{\github}[1]{{\faGithub \hspace{1pt} \href{https://github.com/#1/}{\texttt{#1}}}}

\newcommand{\email}[1]{\faEnvelope \hspace{1pt} \href{mailto:#1}{\texttt{#1}}}

\newcommand{\website}[1]{\faLink \hspace{1pt} \href{http://#1/}{\texttt{#1}}}

\newcommand{\stackoverflow}[2]{\faStackOverflow \hspace{1pt} \href{https://stackoverflow.com/users/#1}{\texttt{#2}}}

\newcommand{\linkedin}[1]{{\faLinkedin \hspace{1pt} \href{https://www.linkedin.com/in/#1/}{\texttt{#1}}}}


\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Mohammad Ganji} \\ \vspace{5pt}
    \small 
        \website{m.ganji.blog}
    \hspace{1pt} $|$ \hspace{1pt}
        \github{mohganji}
    \hspace{1pt} $|$ \hspace{1pt} 
        \email{mohganji97@gmail.com}
    \hspace{1pt} $|$ \hspace{1pt} 
        \linkedin{mohganji}
    \hspace{1pt} $|$ \hspace{1pt} 
        \stackoverflow{7025986/mo-ganji}{>1000 reputation}
    \\ \vspace{-3pt}
\end{center}

%-------------SUMMARY------------
\section{About}

\resumeItemListStart
    \aboutItem{Thesis-based Master student at SFU, with a focus on debugging and testing asynchronous software. }
    \aboutItem{Worked 3 years as a software engineer. Also built, shipped, and maintained 5+ freelance and personal projects.}
    \aboutItem{Developed, maintained, and revamped 5 back-end services, in micro-services and monolithic architectures.}
    \aboutItem{Designed, improved, and optimized databases for 4 services. Worked with SQL(PostgreSQL) and noSQL(MongoDB, Redis). Optimized tables with +100m records.}
    \aboutItem{Actively engaged in cross-team communications with dev teams, sales, product owners, and account managers.}
    \aboutItem{Contributed in hiring: mentorship, tech interviews and code reviews.}
    % \aboutItem{I also maintain a blog \href{https://m.ganji.blog}{\small \faExternalLink*}. It's my little shelf on the corner of the internet.}
\resumeItemListEnd
        

%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
       \textbf{Languages}{: Python, Typescript, JavaScript, SQL, Java, C++, MongoDB, HTML/CSS} \vspace{2pt} \\
       \textbf{Knowledge}{: Design Patterns, Database Design, Object Oriented Design, Microservice Architecture, Mentoring, Linux Servers, Problem Solving, Data Structures and Algorithms } \vspace{2pt} \\
       \textbf{Frameworks \& Tools}{: Django Rest Framework, Redis, Node.js, React.js, Git, Docker, Nginx, Trello, ELK Stack, Grafana}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{PROFESSIONAL EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Yektanet - The largest online advertising platform in Iran (+250 employees) \href{https://en.yektanet.com}{\small \faExternalLink*}}{Dec. 2019 -- Dec. 2020 (1yr)}
      {Software Engineer - Push Notification Ads Service}{Tehran, IR}
      \resumeItemListStart
        \resumeItem{Refactored push micro-service; Designed and implemented a more maintainable and extensible architecture utilizing OOD and Design Patterns; This allowed scaling to 100M daily push notifications and 20x more revenue in 1 year.}
        \resumeItem{Developed and maintained 50+ APIs using Django Rest Framework; Improved average response time to 75\%.}
        \resumeItem{Optimized push database(100M+ records, 20+ tables in PostgreSQL) by rewriting complex queries, improving indexing, caching and in memory optimizations(on Redis) and automated clustering; Reduced query time by 80\%.}
        \resumeItem{Managed product release and launch of CPC push feature; Generated over 30\% of the revenue of push ads service.}
        \resumeItem{Created and maintained a dashboard of 20+ charts for debugging using ELK Stack.} 
        \resumeItem{Conducted interviews for 5 applicants, mentored 3 interns, reviewed 100+ resumes and 100+ coding tasks.}
      \resumeItemListEnd

    \resumeSubheading
      {Pheebs - Mobile Apps Startup}{Sep. 2017 -- Nov. 2019 (2yrs)}
      {Full Stack Developer}{Tehran, IR}
      \resumeItemListStart
        \resumeItem{Worked on server-side development of 2 mobile applications, Chizz(120k+ monthly active users) and Episode(20k+ users) using Node.js,  Express.js, and Graphql in teams of 4\textasciitilde5.}
        \resumeItem{Developed admin panel, landing page, and web views for Episode and Chizz, using React.js, HTML/CSS, jQuery.}
        \resumeItem{Implemented database models \& caching(30+ collections) using MongoDB,  Mongoose, and Redis. }
        \resumeItem{Wrote and maintained unit and integration tests for Chizz \& Episode using Jest.}
        \resumeItem{Set up deployment automation for Episode using Docker and Nginx on Linux servers.}
        % \resumeItem{Maintained Metabase dashboards for data analysis;}

    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Simon Fraser University}{Sep. 2020 -- Dec. 2022 (expected)}
      {M.S. in Computer Science, Current GPA: 3.89/4.00, Advisor: Saba Alimadadi Jani \href{https://www.sfu.ca/computing/people/faculty/sabaalimadadi.html}{\small \faExternalLink*}}{Burnaby, CA}
      	\resumeItemListStart
    	\resumeItem {\textbf{Research Areas}: Dynamic analysis, asynchronous programming, practical software engineering}
    	\resumeItem {\textbf{TA Experience}: CMPT276 (Intro to Software Engineering); CMPT120 (Intro to Computer Science and Programming)}
    % 	\resumeItem {\textbf{Expected Graduation Date}: Dec. 2022}
        \resumeItemListEnd
        
    \resumeSubheading
      {University of Tehran}{Sep. 2015 -- May. 2020}
      {B.S. in Software Engineering, GPA: 3.40/4.00}{Tehran, IR}
      	\resumeItemListStart
        \resumeItem {\textbf{Thesis}: "Real-time verification and evaluation of algorithms efficiency in distributed actor based systems"}
        % \resumeItem {\textbf{TA Experience}: Design \& Analysis of Algorithms (5 terms); Design of Programming Languages \& Compilers}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------

\section{PROJECTS}
    \resumeSubHeadingListStart
        
        \resumeProjectHeading 
          {\textbf{BlogFrog.xyz} - A place to discover new random blog posts on the internet. \href{http://blogfrog.xyz}{\small \faExternalLink*}} 
          {Jul. 2022 - Now} 
          {Burnaby, CA} \vspace{-8pt}
          
        \resumeProjectHeading
          {\textbf{m.ganji.blog} - My Personal Website \href{http://m.ganji.blog}{\small \faExternalLink*}} 
          {Mar. 2022 -- Now} 
          {Burnaby, CA} \vspace{-8pt}
          
        \resumeProjectHeading
          {\textbf{In-Lab Exam Scheduler Platform} - Contract Job} 
          {Jun. 2021 -- Sep. 2021} 
          {Burnaby, CA} \vspace{-8pt}
          \resumeItemListStart 
            \resumeItem{Developed a web platform to automate scheduling in-lab testing at SFU CSIL labs using Express.js, Nginx, PostgreSQL, and EJS.}
          \resumeItemListEnd 
          
        \resumeProjectHeading 
          {\textbf{SchemaIran Telegram bot} - Freelance Project \href{https://t.me/SchemaIran_Bot}{\small\faExternalLink*}}
          {Mar. 2017 -- Now}
          {Tehran, IR} \vspace{-8pt}
          \resumeItemListStart
            \resumeItem{Developed a Telegram bot for Schemairan \href{https://schemairan.ir}{\small \faExternalLink*} clinic to conduct Young Schema Questionnaire \href{https://doi.org/10.1037/t67023-000}{\small \faExternalLink*} using Node.js and MongoDB; Collected 5k+ test results.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
